Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2019-02-05 doc/network.tex
A few more comments

In general, there are two factors that cause spatial reduction in the mean generation interval: local spatial effects (e.g., in a household or neighborhood) and (2) population-level effects; 
the latter effect provides an equivalent explanation for the underestimation of the mean generation interval, sampled across an entire epidemic (\fref{censor}). \jd{I'll have to think about this, or you'll have to explain.}
Although the effect of the overall depletion of susceptible individuals is relatively well-understood \citep{champredon2015intrinsic}, estimating the local effects on observed generation intervals is expected to be a hard problem on realistic networks. 
\cite{tomba2010some} showed that an analytical expression for the mean generation interval, which takes into account the local spatial effect, can be derived for a household with one primary case and two susceptible individuals, but solving for higher order structures seems both infeasible and impractical.
\jd{The global spatial effect is sort of the non-spatial effect: the overall response to decreasing susceptibles, like in Champredon.}
\swp{Tried to fix this}

@@

When generation intervals are sampled through contact tracing, there will be four effects present in the sample: (1) right-censoring effect, (2) egocentric effect, (3) local spatial effect and (4) mean susceptible-depletion effect.
We can correct explicitly for the egocentric effect and, in the case of exponential growth, the right-censoring effect.
While the other two effects are difficult to measure, we can make qualitative predictions about their effects on the realized generation intervals and reproductive number. 
Both local spatial and susceptible depletion effects reduce number of infections that occur and shorten generation intervals but the time scale on which they matter differs:
local spatial effect will be important early in an epidemic whereas the susceptible depletion will be small until sufficient amount of susceptible individuals become infected.
As a result, we expect the initial spread of a disease and the realized reproductive number to be heavily dependent on local spatial and egocentric effects.

>>>>

\jd{I think there's room to be clearer here. All three depletion effects are similar. Should we call them all depletion?: egocentric, local, global?} In general, there are two factors that cause spatial reduction in the mean generation interval: local spatial effects (e.g., in a household or neighborhood) and (2) population-level effects; 
the latter effect provides an equivalent explanation for the underestimation of the mean generation interval, sampled across an entire epidemic (\fref{censor}). \jd{I'll have to think about this, or you'll have to explain.}
Although the effect of the overall depletion of susceptible individuals is relatively well-understood \citep{champredon2015intrinsic}, estimating the local effects on observed generation intervals is expected to be a hard problem on realistic networks, although there has been interesting work on spatial cases, particularly on hierarchical networks of households nested within communities (e.g.,  \cite{tomba2010some}). \jd{Don't think we need more than that about Tomba; I wonder if any of Frank Ball's household work could be relevant.}
\jd{The global spatial effect is sort of the non-spatial effect: the overall response to decreasing susceptibles, like in Champredon.}
\swp{Tried to fix this}
\jd{K. I've added at least one new comment in this direction Feb 05 (Tue).}

@@

When generation intervals are sampled through contact tracing, there will be four effects present in the sample: (1) right-censoring effect, (2) egocentric effect, (3) local spatial effect and (4) mean susceptible-depletion effect.
We can correct explicitly for the egocentric effect and, in the case of exponential growth, the right-censoring effect.
While the other two effects are difficult to measure, we can make qualitative predictions about their effects on the realized generation intervals and reproductive number. 
\jd{How about: Both local and global depletion\ldots?}
Both local spatial and susceptible depletion effects reduce number of infections that occur and shorten generation intervals but the time scale on which they matter differs:
local spatial effect will be important early in an epidemic whereas the susceptible depletion will be small until sufficient amount of susceptible individuals become infected.
As a result, we expect the initial spread of a disease and the realized reproductive number to be heavily dependent on local spatial and egocentric effects.
